Packing Boxes with Score Constraints

### 2017-08-29 docs/main.tex
updated MGTMA

Initially, we create 18 random values between 1 and 70, which will be our score widths. We also need to add an extra box with two score of widths 70mm, which will be our ``dominating scores'', giving us a total of 10 boxes and 20 scores. These dominating scores will eventually be discarded.

@@

% Modified matching

\begin{table}[htb]
	\centering
	\begin{tabular}{|c|c|}
		\hline
		\multicolumn{2}{|c|}{Match}\\ \hline
		0 & 19 \\ \hline
		1 & 18 \\ \hline
		2 & 17 \\ \hline
		3 & 16 \\ \hline
		4 & 15 \\ \hline
		5 & 14 \\ \hline
		6 & 13 \\ \hline
		7 & 11 \\ \hline
		8 & 12 \\ \hline
		9 & 10 \\
		\hline
	\end{tabular}
	\caption{Match List.}
\end{table}

>>>>

Initially, we create 18 random values between 1 and 70, which will be our score widths. We also need to add an extra box with two score of widths 70mm, which will be our ``dominating scores'', giving us a total of $n$ = 10 boxes and 20 scores. These dominating scores will eventually be discarded.

@@

\subsection{Matching scores}
Once we have created the problem instance, we then have to attempt to match the scores together. If two scores can be matched, it means that the boxes can be placed next to each other, and the total width of the two scores from the boxes is equal to or exceeds the threshold, and can therefore be scored using the knives in the scoring machine.

The matching is performed as follows: starting from the smallest score (0), we attempt to match it with the largest possible score it is adjacent to ( = 1 in the adjaceny matrix), and that has not yet been matched (in this case, 19). We continue until all scores have been matched. If a score cannot be matched due to the largest score being its mate, we match the score with the second largest score available. As we can see in Table \ref{table:match}, score 7 was unable to be matched with the largest possible score, 12, as they are mates. Instead, 7 was matched with the next largest score, 11.

Once the matching algorithm is complete, we then examine the size of the matching list. For the instance to be feasible, all of the scores must be matched. If not all of the scores are matched, i.e. there are less than $n$ matchings in the matching list, then there are not enough matching edges to create a path, and the instance is infeasible.

\begin{table}[htb]
	\centering
	\begin{tabular}{|c|c|}
		\hline
		\multicolumn{2}{|c|}{Match}\\ \hline
		0 & 19 \\ \hline
		1 & 18 \\ \hline
		2 & 17 \\ \hline
		3 & 16 \\ \hline
		4 & 15 \\ \hline
		5 & 14 \\ \hline
		6 & 13 \\ \hline
		7 & 11 \\ \hline
		8 & 12 \\ \hline
		9 & 10 \\
		\hline
	\end{tabular}
	\caption{Match List.}
	\label{table:match}
\end{table}

\subsection{Mate-Induced Structure}
